Paper Five Summary

### 2015-10-20 hw/read/5/summary.tex
Added two more improvements

\section*{Possible Improvements}
\begin{itemize}
\item The phrasing in particular sections is grammatically incorrect. Here are a couple examples: "The deeper in the tree is the ownership the more focused the activities, communication, and responsibility" (pg. 4) and "The lower level is the ownership the better is the quality" (pg. 5). More editing should have been done to fix these errors.
\end{itemize}

>>>>

\section*{Possible Improvements}
\begin{itemize}
\item The phrasing in particular sections is grammatically incorrect. Here are a couple examples: "The deeper in the tree is the ownership the more focused the activities, communication, and responsibility" (pg. 4) and "The lower level is the ownership the better is the quality" (pg. 5). More editing should have been done to fix these errors.
\item The authors don't address how the size of a binary affects the probability measure of software defects. It can be logically deduced that larger binaries inherently have a greater number of defects.
\item The authors address the validity of their features using step-wise regression and PCA but it would also be beneficial if the authors presented this data and gave a ranking of the affect of the features on predicting variance.
\end{itemize}
